### 2017-09-29 TF-vldb2018/sec-dynamicTopk.tex

\section{A Unified Incremental Method}
\label{sec-dynamictopk}

\revise{
%In last section, we have studied the top-$k$ team formation problem.
Based on the dynamic top-$k$ team formation problem defined in Section~\ref{subsec-dynteamF}, 
in this section, we first theoretically analyze the challenges and design principles, 
and then develop a unified incremental framework for \dynteamF.
For convenience, the notations used are summarized in Table~\ref{tab-notation}.}

@@

\begin{table}[tb!]
	%\vspace{-2ex}
	%\vspace{2ex}
	\begin{center}
		\begin{small}
			%\vspace{-2ex}
			\scriptsize
			\begin{tabular}{|c|l|}
				\hline
				{\bf Notations}             &  {\bf Description}     \\
				\hline\hline
				$P,G$                     &  pattern and data graphs       \\ \hline
				$\ball{[v, r]}$              &  a ball in $G$ with center node $v$ and radius $r$  \\ \hline
				$L_k(P, G)$                  &  the list of top-$k$ perfect subgraphs in $G$ for $P$  \\ \hline
				$\Delta P, \Delta G$       &  pattern and data updates       \\ \hline
				$\oplus$                    &  applying updates $\Delta P$ and $\Delta G$ to $P$ and $G$       \\ \hline
				${\cal P}_{h}=\{P_{fi}, C\}$     &  pattern fragmentation: $h$ fragments and cut    \\ \hline
				$\affballsx$                &  affected balls       \\ \hline
				$M(P_{fi}, \ball{[v,r]})$    &  the maximum match relation in $\ball{[v,r]}$ for $P_{fi}$   \\ \hline
				$\tilde{M}(P,G)$            &  fragment-ball matches (auxiliary structure)     \\ \hline
				$\fs$, $\bs$              &  fragment status, ball status (auxiliary structure) \\    \hline
				$\fb$                       &  fragment-ball-match index, containing $\fs, \bs$ \\    \hline
				$\bfc$, $\upl$              &  ball filter, update planner (auxiliary structure) \\    \hline
			\end{tabular}
			\vspace{-2ex}
		\end{small}
		\caption{Notations}
		\label{tab-notation}
		\vspace{-6ex}
	\end{center}
\end{table}

@@

%\subsection{A Unified Incremental Approach}
%\label{subsec-framework}

@@

\vspace{-0.5ex}
However, $P$ and $h$ are typically small in practice~\cite{FanLMTWW10}, \eg $|P|=15$ and $h=3$.
In light of this, we give a heuristic algorithm, denoted by \kw{PFrag}, for the problem, and is shown in the Appendix.
\kw{PFrag} works by connecting pattern fragmentation to the widely studied {\sc $(k, \nu)$-Balanced Partition} problem \cite{AndreevR06},
which is not approximable in general, but has efficient and sophisticated heuristic algorithms~\cite{metis-KarypisK98a}.

>>>>

\section{A Unified Incremental Solution}
\label{sec-dynamictopk}

In this section, we first analyze the challenges and design principles of dynamic top-$k$ team formation,
and then develop a unified incremental framework for \dynteamF.
For convenience, the notations used are summarized in Table~\ref{tab-notation}.

\subsection{Analyses of Dynamic Team Formation}

@@

\begin{table}[tb!]
	%\vspace{-2ex}
	%\vspace{2ex}
	\begin{center}
		\begin{small}
			%\vspace{-2ex}
			\scriptsize
			\begin{tabular}{|c|l|}
				\hline
				{\bf Notations}             &  {\bf Description}     \\
				\hline\hline
				$P,G$                     &  pattern and data graphs       \\ \hline
				$\ball{[v, r]}$              &  a ball in $G$ with center node $v$ and radius $r$  \\ \hline
				$L_k(P, G)$                  &  the list of top-$k$ perfect subgraphs in $G$ for $P$  \\ \hline
				$\Delta P, \Delta G$       &  pattern and data updates       \\ \hline
				$\oplus$                    &  applying updates $\Delta P$ and $\Delta G$ to $P$ and $G$       \\ \hline
				${\cal P}_{h}=\{P_{fi}, C\}$     &  pattern fragmentation: $h$ fragments and cut    \\ \hline
				$\affballsx$                &  affected balls       \\ \hline
				$M(P_{fi}, \ball{[v,r]})$    &  the maximum match relation in $\ball{[v,r]}$ for $P_{fi}$   \\ \hline
				$\tilde{M}(P,G)$            &  fragment-ball matches (auxiliary structure)     \\ \hline
				$\fs$, $\bs$              &  fragment status, ball status (auxiliary structure) \\    \hline
				$\fb$                       &  fragment-ball-match index, containing $\fs, \bs$ \\    \hline
				$\bfc$, $\upl$              &  ball filter, update planner (auxiliary structure) \\    \hline
			\end{tabular}
			\vspace{-1ex}
		\end{small}
		\caption{Notations}
		\label{tab-notation}
		\vspace{-6ex}
	\end{center}
\end{table}

@@

\subsection{A Unified Incremental Approach}
%\label{subsec-framework}

@@

\vspace{-0.5ex}
However, $P$ and $h$ are typically small in practice~\cite{FanLMTWW10}, \eg $|P|=15$ and $h=3$.
In light of this, we give a heuristic algorithm, denoted by \kw{PFrag}, for the problem, and is shown in the
full version~\cite{fullvldb18}.
\kw{PFrag} works by connecting pattern fragmentation to the widely studied {\sc $(k, \nu)$-Balanced Partition} problem \cite{AndreevR06},
which is not approximable in general, but has efficient and sophisticated heuristic algorithms~\cite{metis-KarypisK98a}.
